\batcave: Calling somatic mutations with a tumor- and site-specific prior

### 2019-12-16 ResponseToReviews.tex

We discuss this issue in a new paragraph in Discussion.
\end{response}

In Rubanova et al ( https://www.biorxiv.org/content/10.1101/260471v4.full), it is argued that there are changes in mutational signatures over time in cancers. While Mannakee and Gutenkunst mention this work, they should further comment on whether such changes in mutational signatures over time are small enough to be explained by the BATCAVER concept of re-evaluating mutations based on p-value.
\begin{response}
\RNG{Going to be difficult, depending on biology to offer specific guidance about the size of the change. Rather, we now do a goodness-of-fit test and warn the user if it looks like it's violated.}
\BKM{We could detect a change above. Whether it matters or not is a complex interplay between depth and selection. For late changes most mutations with that signature will be below the threshold of detection. For an early mutation all of the marginal (low frequency) variants will be from the signature.}
\end{response}

Minor
p.2: “Folding the central base to the pyrimidines”: The “folding” terminology is not standard and should be improved. 
\begin{response}
Corrected
\end{response}

Equation 11: This equation is not correct if there is subclonal copy number evolution that changes the distribution of mutations above the allele frequency threshold. The authors should more clearly state this assumption.
\begin{response}
The reviewer is correct, although a large number of copy number changes would be necessary to substantially bias the estimated mutation rate.
Potential future work could incorporate external copy number calls to improve the estimate of the point mutation rate.

### 2019-12-16 NAR_DRAFT.tex
Add response regarding copy number changes

>>>>

\rngcomment{
To estimate the tumor mutation rate, \batcave uses a model of the distribution of variant allele frequencies  generated during exponential growth (Eq.~\ref{eqn:mut_rate}).
Mutations that change copy number might distort the empirical allele frequency distribution, biasing the estimate.
But substantially biasing the estimate would require copy number changes in a large number of genomic regions.
Nevertheless, a potential extension of the \batcave algorithm would be to incorporate external copy number calls in order to adjust allele frequencies before estimating the mutation rate.
}
